Efficiently stable presentations from error-correcting codes

### 2023-10-27 efficient_stability.tex
small note

Can such ``efficient'' presentations of $G(h)$ still be stable? The naive approach, of extending an $\eps$-approximate homomorphism of $G(h)=\langle S:R\rangle$ into an $\eps'$-approximate homomorphism of the multiplication table presentation of $\Z_2^k$, leads to $\eps'=\Omega(k^2\eps)$ and hence a logarithmic dependence of the modulus of stability on the group size. Is it possible to do better? Glebsky's result for the case of $\Z^2$ mentioned earlier suggests that it is in some cases  possible -- but in what generality? \mnote{Actually, we have a lower bound on the stability rate of $\Z^d$. It is $\Omega(\eps^{1/d})$ by a work of Becker and Mosheiff (they look at the permutation setup, but their example works for unitaries). Thus, there is not better solution in general, without assuming that all the generators are involutions. I just sent to John this draft, and by how he was confused by this paragraph, and the fact the the last question is known to be flase, we should rewrite it.}

>>>>

Can such ``efficient'' presentations of $G(h)$ still be stable? The naive approach, of extending an $\eps$-approximate homomorphism of $G(h)=\langle S:R\rangle$ into an $\eps'$-approximate homomorphism of the multiplication table presentation of $\Z_2^k$, leads to $\eps'=\Omega(k^2\eps)$ and hence a logarithmic dependence of the modulus of stability on the group size. Is it possible to do better? Glebsky's result for the case of $\Z^2$, which is an infinite group, suggests that in some cases the modulus of stability can be independent of the group size. It is therefore not clear what if any of the known group parameters should play a role in it in general.  
 \mnote{Actually, we have a lower bound on the stability rate of $\Z^d$. It is $\Omega(\eps^{1/d})$ by a work of Becker and Mosheiff (they look at the permutation setup, but their example works for unitaries). Thus, there is not better solution in general, without assuming that all the generators are involutions. I just sent to John this draft, and by how he was confused by this paragraph, and the fact the the last question is known to be flase, we should rewrite it.}\tnote{Ok, I edited a bit}
